---
title: "PEC 2 - Estudio de técnicas de visualización de datos"
author: "Irene López Ruiz"
date: "13/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Scatter plot

## Annual money spent on wine

Scatter plot to show correlation between annual income and the consume of wine.

Data is available at https://www.kaggle.com/jackdaoud/marketing-data

```{r}
library(tidyverse)
library("ggplot2")

# Read and preprocess data
data_wine<-read.csv("marketing_data.csv", header=T, 
                    sep=",", na.strings = "")
data_wine <- data_wine %>%
  select(Income, MntWines) %>%
  mutate_at(vars(1), funs(gsub(",|\\$", "", .))) %>% 
  filter(complete.cases(.))

# Create the plot
scatter <- ggplot(data_wine, aes(x=Income, y=MntWines)) + 
  geom_point(size=1, alpha=0.5) +
  labs(title="Money spend on wine in the last year",
       x="Annual Income ($)", y = "Amount spent on wine ($)") + 
  theme_classic()

# 1. Open png file
png(file="ScatterPlot.png", width = 350, height = 350)

# 2. Add plot to file
scatter

# 3. Close the file
dev.off()

# Display plot
scatter 
```

# Ridgline plot

## Distributions of money spent on wine in different education levels

```{r}
library(ggridges)
library(ggplot2)

# Read and preprocess data
data_wine<-read.csv("marketing_data.csv", header=T, 
                    sep=",", na.strings = "")
data_wine[, "Country"] <- as.factor(data_wine[, "Country"])
data_wine[, "Education"] <- as.factor(data_wine[, "Education"])

# Create plot
ridgeline <- ggplot(data_wine, aes(x = MntWines, y = Education, fill = Education)) +
  geom_density_ridges(alpha=0.6) +
  theme(legend.position = "none",
        panel.spacing = unit(0.1, "lines"),
        strip.text.x = element_text(size = 8)) +
  labs(title="Wine consume in USA", x="Money spent ($)", y="Education level")

# 1. Open png file
png(file="RidglinePlot.png", width = 350, height = 350)

# 2. Add plot to file
ridgeline

# 3. Close the file
dev.off()

# Display plot
ridgeline
```


# Sunburst plot

## Shows available on Netflix

Sunburst plot of Netflix contents available in the top 5 content countries since 2017.
Hover over the plot to see each category label and proportion. 

Data is available at https://www.kaggle.com/shivamb/netflix-shows

```{r}
library(sunburstR)

# Read and preprocess data
data<-read.csv("netflix_titles.csv", header=T, sep=",",
               na.strings = "")
data <- data[complete.cases(data[ , 6]),]
cols <- c("type", "country", "rating", "release_year")
data[cols] <- lapply(data[cols], factor)

# Create plot
content <- data %>%
  select(country, release_year, type) %>%
  mutate_at(vars(2,3), funs(gsub("-", "_", .))) %>% 
  filter(country %in% names(sort(table(data$country), decreasing=TRUE)[1:5]) & 
           release_year >= 2017) %>%
  mutate(
    path = paste(country, type, release_year, sep = "-")
  ) %>%
  slice(2:100) %>%
  mutate(
    V2 = 1
  )
sunburst_plot <- sunburst(data = data.frame(xtabs(V2~path, content)), 
                          legend = FALSE, 
                          colors = c("D99527", "6F7239", "CE4B3C", "C8AC70", 
                                     "018A9D"))

# Display plot
sunburst_plot
```

